A general and efficient representation of Ancestral Recombination Graphs

### 2022-08-24 paper.tex
Authorship

\linenumbers
\title{A general and efficient representation of Ancestral Recombination Graphs}
% First authors
\author{Author McAuthorface}
% Corresponding

>>>>

\linenumbers
\title{A general and efficient representation of Ancestral Recombination Graphs}

% First authors
\author[1]{Yan Wong}

% Second authors
\author[2,$\star$]{Anastasia Ignatieva}
\author[3,$\star$]{Jere Koskela}

% Middle Authors
\author[4]{Gregor Gorjanc}
\author[5]{Anthony W. Wohns}

% Corresponding
\author[1,$\dagger$]{Jerome Kelleher}

\affil[1]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, University of Oxford, OX3 7LF, UK}
\affil[2]{Department of Statistics, University of Oxford, OX1 3LB, UK}
\affil[3]{Department of Statistics, University of Warwick, CV4 7AL, UK}
\affil[4]{The Roslin Institute and Royal (Dick) School of Veterinary Studies, University of Edinburgh, EH25 9RG, UK}
\affil[5]{Broad Institute of MIT and Harvard, Cambridge, MA 02142, USA}

\affil[$\star$]{Denotes shared second authorship, listed alphabetically}
\affil[$\dagger$]{Denotes corresponding author}
